Adopting agile software development in the large organizations: A systematic literature review

### 2014-08-10 journal/content.tex
Style review

        \bottomrule
    \end{tabular}
    \caption{Context information}
    \label{table:contextualcodes}
\end{table}

@@

        \bottomrule
    \end{tabular}
    \caption{Code families}
    \label{table:codefamilies}
\end{table}

@@

\begin{table}[t]
    \centering
    \begin{tabular}{ l r r }
        \toprule
        Code family    &  Codes  &  Quotations
        \\
        \midrule
        RQ1: Reason to change &        30 &  123 \\
		RQ2: Transformation process &  16 &  580 \\
		RQ3: Challenges &              40 &  323 \\
		RQ3: Success factors &         44 &  260 \\
		Investing in change  &          5 &  137 \\
		Practices &                    11 &  170 \\
		Contextual &                    8 &  215 \\
		Total &                       154 & 1575 \\
        \bottomrule
    \end{tabular}
    \caption{Number of codes and quotations per code family}
    \label{table:codecount}
\end{table}

@@

A typical practice was creating some internal material promoting the new agile
model. The material served both a documenting role and promoted awareness for
the new development model. The material was created to help explaining the agile
model to stakeholders, and to serve as a reference for teams implementing it.
Typical in-house agile material was a manual which presented the organization
specific implementations of agile practices [P1]. Many cases described using a
wiki-based website to maintain and distribute information on agile practices
[P14, P16, P45]. Hanly et al. [P23] describes how a n organization specific
cookbook for agile implementation was created. The cookbook resolved
misconceptions, presented differences between the old model and agile, and
described agile development in traditional terms [P23]. Other agile material
organizations produced were short videos [P32], and a branded theme for the new
process [P8]. One primary source provided the organization specific Agile Policy
as an appendix [P26].

@@

\begin{table}[h]
    \centering
    \begin{tabular}{ l l }
        \toprule
        Factors of investment and resourcing  &  Described in \\
        \midrule
        Lack of coaching                      &  P1, P6, P23, P45, P47, P49  \\
        Lack of training                      &  P11, P20, P45  \\
        Excessive commitment of people        &  P37, P42, P49  \\
        Old commitments are kept              &  P11, P21  \\
        Physical spaces can not be rearranged  &  P6, P14, P29, P36, P38, P49  \\
        \bottomrule
    \end{tabular}
    \caption{Summary of investment and resourcing factors that affect
             transformation negatively}
    \label{table:challenges_lackofinvestment}
\end{table}

@@

\begin{table}[b]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.56\textwidth}
                     >{\raggedright\arraybackslash}p{0.36\textwidth} }
        \toprule
        Challenges relating to large scale  &  Described in \\
        \midrule
        Management roles unclear in agile       &  P2, P11, P27, P30, P38, P49, P52 \\
        Using old and new models side by side   &  P1, P8, P10, P26, P29 \\
        Management uses waterfall model         &  P3, P6, P35, P38, P45, P46 \\
        Duplicating management with two models  &  P20, P48 \\
        Agile models diverge between teams      &  P8, P9, P38, P43, P48 \\
        Internal boundaries in organization     &  P10, P11 \\
        \bottomrule
    \end{tabular}
    \caption{Summary of challenges relating especially to large scale}
    \label{table:challenges_largescale}
\end{table}

>>>>

        \bottomrule
    \end{tabular}
    \caption{Context information specified to be gathered from primary studies.}
    \label{table:contextualcodes}
\end{table}

@@

        \bottomrule
    \end{tabular}
    \caption{Code families defined before start of coding. Examples on
    potential codes to be inducted in parentheses.}
    \label{table:codefamilies}
\end{table}

@@

\begin{table}[t]
    \centering
    \begin{tabular}{ l r r }
        \toprule
        Code family    &  Codes  &  Quotations
        \\
        \midrule
        RQ1: Reason to change &        30 &  123 \\
		RQ2: Transformation process &  16 &  580 \\
		RQ3: Challenges &              40 &  323 \\
		RQ3: Success factors &         44 &  260 \\
		Investing in change  &          5 &  137 \\
		Practices &                    11 &  170 \\
		Contextual &                    8 &  215 \\
		Total &                       154 & 1575 \\
        \bottomrule
    \end{tabular}
    \caption{Number of codes and quotations per code family, as the final result
    of coding the primary studies}
    \label{table:codecount}
\end{table}

@@

A typical practice was creating some internal material promoting the new agile
model. The material served both a documenting role and promoted awareness for
the new development model. The material was created to help explaining the agile
model to stakeholders, and to serve as a reference for teams implementing it.
Typical in-house agile material was a manual which presented the organization
specific implementations of agile practices [P1]. Many cases described using a
wiki-based website to maintain and distribute information on agile practices
[P14, P16, P45]. Hanly et al. [P23] describes how an organization specific
cookbook for agile implementation was created. The cookbook resolved
misconceptions, presented differences between the old model and agile, and
described agile development in traditional terms [P23]. Other agile material
organizations produced were short videos [P32], and a branded theme for the new
process [P8]. One primary source provided the organization specific Agile Policy
as an appendix [P26].

@@

\begin{table}[b]
    \centering
    \begin{tabular}{ l l }
        \toprule
        Factors of investment and resourcing  &  Described in \\
        \midrule
        Lack of coaching                      &  P1, P6, P23, P45, P47, P49  \\
        Lack of training                      &  P11, P20, P45  \\
        Excessive commitment of people        &  P37, P42, P49  \\
        Old commitments are kept              &  P11, P21  \\
        Physical spaces can not be rearranged  &  P6, P14, P29, P36, P38, P49  \\
        \bottomrule
    \end{tabular}
    \caption{Summary of investment and resourcing factors that affect
             transformation negatively}
    \label{table:challenges_lackofinvestment}
\end{table}

@@

\begin{table}[t]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.56\textwidth}
                     >{\raggedright\arraybackslash}p{0.36\textwidth} }
        \toprule
        Challenges relating to large scale  &  Described in \\
        \midrule
        Management roles unclear in agile       &  P2, P11, P27, P30, P38, P49, P52 \\
        Using old and new models side by side   &  P1, P8, P10, P26, P29 \\
        Management uses waterfall model         &  P3, P6, P35, P38, P45, P46 \\
        Duplicating management with two models  &  P20, P48 \\
        Agile models diverge between teams      &  P8, P9, P38, P43, P48 \\
        Internal boundaries in organization     &  P10, P11 \\
        \bottomrule
    \end{tabular}
    \caption{Summary of challenges relating especially to large scale}
    \label{table:challenges_largescale}
\end{table}
